\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-09-04 doc/sw-system.tex
Closed #70 with some brief discussion of nervous classifers in capacity subsection of discussion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
\caption{Predictability of final skill from early skill (after 10 training
classifications) in stage 1 agents. The dashed lines enclose 649 agents with
early skill greater than 0.1 
who retain final skill of greater than 0.05. Point size is proportional to
contribution (plus a constant).}
\label{fig:crowd:skillprediction}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Having seen the importance of the high skill volunteers at both stage 1 and
stage 2, we might ask, can we predict agent skill after, say, the volunteer
has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
plot this ``early skill'' against final skill, for all experienced stage 1
volunteers. The majority of the crowd shows little correlation, but at the
high early skill end, some predictability appears. The 649 experienced  stage
1 volunteers who had early skill greater than 0.1 went on to attain a mean
final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
suggests that it might be worth tracking volunteers' skill as a project
progresses, in order to encourage those showing an aptitude for the task to
take part in the more difficult activities, such as stage 2 refinement.
However, this would not have done a very good job at identifying the 
volunteers who went on to make the largest contributions: the point size in 
\Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
many of the highest contributors showed relatively low skill early on.

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both stage 1 and 2 of the CFHTLS project, with the
total numbers of agents and subjects for comparison.  These numbers allow us
to quantify the efficiency of the system.  The contribution per classification
is defined in terms of a hypothetical subject with lens probability of 0.5;
one bit of information is needed to update such a subject's lens probability
to either zero or one. This means that a maximally complete classification
stage would yield a total contribution (summed over all agents) equal to the
number of subjects. The ratio of this hypothetical optimum to the actual total
contribution is therefore a measure of the stage's inefficiency. We find our
inefficiency (by dividing column 2 by column 3) to be 33\% and 17\% in stage 1
and 2 respectively. In stage 1, this inefficiency is due to the daily
processing: we were not able to retire subjects fast enough, and so they,
remained in the system, being over-classified. Indeed, only 3705745
classifications were needed to retire all the subjects: the ratio of this to
the total number made is 34\%. (The remaining 1\% is due to not all subjects
being classified to 1 or 0 probability.) At stage 2, we did not retire any
subjects at all; the inefficiency in this case was by design, to give everyone
a chance to appreciate what they had found together!

The total skill of the crowd, computed by summing the skill of all the agents,
is, similarly, a measure of the effective crowd size: a crowd of perfect
classifiers would be this size. The stage 1 crowd was equivalent to a team of
1469.9 perfect classifiers; the stage 2 crowd was equivalent to a team of
102.4 perfect classifiers.

The total information generated during the survey is harder to interpret,
because it's exactly the high probability candidates that we leave in the
system that give rise to most of the information generated. What we can do is
divide the total information generated by the amount of information it takes
to classify a \sw subject all the way to the detection threshold (lens
probability 0.95), divide by this number, and then multiply by the survey
inefficiency to get a very rough estimate for the effective number of
detections corresponding to the crowd's contribution. With a prior probability
of $2\times10^{-4}$, it takes 12.3 bits to make a detection (see
\Sref{sec:appendix:infogain} in the appendix); the effective
number of detections contributed by the stage 1 and stage 2 volunteers is then
2830 and 25 bits respectively. 
These figures are close to the numbers of detections
given in column 7 of \Tref{tab:crowd:contributions}. 
The uncertainty in the interpretation of the
information generated provides further justification for our focus on the
expected information gain as a measure of volunteer contribution.

@@

@@

Inefficiency. Move to truly online system: web app to analyse classifications
as it goes. Place for weekly offline processing? Recovering false negatives by
``resurrecting'' subjects that scattered down too soon.

@@

Scaling of system. Factors of ten: $10^4$ volunteers, $10^3$ achieve high
skill, $10^2$ make significant contribution. Good project size is few $10^4$
subjects, to enable completion by a crowd of this size in short time.

Ways to increase numbers of high-contribution volunteers: 1) increase crowd
size. Higher exposure through media. Multi-lingual user base - comes with
problems.  2) Increase engagement rate:  feedback from survey teams.

@@

>>>>

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \begin{figure}
% \centering\includegraphics[width=0.9\linewidth]{sw-system-figs/early_vs_final_skill.png}
% \caption{Predictability of final skill from early skill (after 10 training
% classifications) in stage 1 agents. The dashed lines enclose 649 agents with
% early skill greater than 0.1 
% who retain final skill of greater than 0.05. Point size is proportional to
% contribution (plus a constant).}
% \label{fig:crowd:skillprediction}
% \end{figure}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% Having seen the importance of the high skill volunteers at both stage 1 and
% stage 2, we might ask, can we predict agent skill after, say, the volunteer
% has experienced 10 training subjects? In \Fref{fig:crowd:skillprediction} we
% plot this ``early skill'' against final skill, for all experienced stage 1
% volunteers. The majority of the crowd shows little correlation, but at the
% high early skill end, some predictability appears. The 649 experienced  stage
% 1 volunteers who had early skill greater than 0.1 went on to attain a mean
% final skill of 0.22, with 97\% remaining at skill 0.05 or higher. This
% suggests that it might be worth tracking volunteers' skill as a project
% progresses, in order to encourage those showing an aptitude for the task to
% take part in the more difficult activities, such as stage 2 refinement.
% However, this would not have done a very good job at identifying the 
% volunteers who went on to make the largest contributions: the point size in 
% \Fref{fig:crowd:skillprediction} is proportional to contribution (plus a constant):
% many of the highest contributors showed relatively low skill early on.

@@

\Tref{tab:crowd:contributions} shows the total effort, contribution, skill and
information generated in both stage 1 and 2 of the CFHTLS project, with the
total numbers of agents and subjects for comparison.   These numbers allow us
to quantify the efficiency of the system.

The contribution per classification is defined in terms of a hypothetical
subject with lens probability of 0.5; one bit of information is needed to
update such a subject's lens probability to either zero or one. This means
that a maximally complete classification stage would yield a total
contribution (summed over all agents) equal to the number of subjects. The
ratio of this hypothetical optimum to the actual total contribution is
therefore a measure of the stage's inefficiency. We find our inefficiency (by
dividing column 2 by column 3) to be 33\% and 17\% in stage 1 and 2
respectively. In stage 1, this inefficiency is due to the daily processing: we
were not able to retire subjects fast enough, and so they, remained in the
system, being over-classified. Indeed, only 3705745 classifications were
needed to retire all the subjects: the ratio of this to the total number made
is 34\%. (The remaining 1\% is due to not all subjects being classified to 1
or 0 probability.) At stage 2, we did not retire any subjects at all; the
inefficiency in this case was by design, to give everyone a chance to
appreciate what they had found together. (An unwanted side effect of this
policy was noted in \Fref{fig:discuss:performance:stage1vstage2} in the
previous sub-section.)

It is clear that to increase the efficiency of the system we need to reduce
the time lag between the classification being made and its outcome being
analyzed. The optimal way to do this would be to have the web app itself
analyze the classifications in a fully online system. This is under
investigation for future projects. With the classification data being analyzed
in real time, there may still be a place for a daily or weekly offline
analysis: this could potentially reduce the false negative and false positive
rates by ``resurrecting'' subjects that had been retired by the online system
before the agents had time to learn enough about their classifier's high
skill.

@@

Finally, we comment on the size of the first \sw crowd, and how the system
might be scaled up for future surveys. In \Sref{sec:results:crowd} and 
\Tref{tab:crowd:contributions}, a rough picture emerged for the \sw crowd of
it containing a few $10^4$ volunteers, with a few $10^3$ achieving
considerable skill, and a few $10^2$ having the time to make a significant
contribution. Slightly more quantitively, we might note that  the total skill
of the crowd, computed by summing the skill of all the agents, is a measure of
the effective crowd size, in the sense that a crowd of perfect classifiers
would be of this size. By this measure,the stage 1 crowd was equivalent to a
team of 1470 perfect classifiers, while the stage 2 crowd was equivalent to a
team of 102 perfect classifiers. With this same crowd, we can see that surveys
providing a few $10^4$ subjects would be completed quickly, if the high
contribution rate of the current crowd were to be repeated.

There are (at least) two ways in which we might increase the numbers of
high-contribution volunteers for larger projects in future. The first is
simply to increase the total crowd size, and hope that a similar fraction of
volunteers make large contributions. Greater exposure of the website to the
public through mass media woudl help. Another option is to advertise the
project to new groups of volunteers by translating the website into other
languages (something which is now supported by the Zooniverse). A
multi-lingual user base would come with its own set of challenges, especially
in terms of volunteers' continuing training and interactions on Talk.

The second way to scale up the number of high contribution classifiers is to
increase the rate at which new volunteers become dedicated volunteers. Based
on feedback from the wider \sw community, this could potentially be achieved
through closer collaboration with the science team. It's also possible that
the dynamic stage 2 system proposed in the previous section may act as an
incentive to some volunteers to increase their contribution (while gaining
skill in order to ``reach'' stage 2). Reducing the rate at which  new
volunteers lose interest could also play a role. Anecdotally, it seems fairly
common for new volunteers to be wary of classifying at all, for fear of
introducing errors. Better explanation of how their early classifications are
analyzed could help assuage these fears: \Sref{sec:results:crowd} shows that
effectively down-weighting new users' classifications (by setting their
agents' initial confusion matrix elements to those of a random classifier)
leads to best performance, a result which shoudl be of some comfort to the
nervous volunteer.

@@

The total information generated during the CFHTLS project is shown in
\Tref{tab:crowd:contributions}. Interpreting these numbers is not easy, but we
might do the following. Dividing this by the amount of information it takes to
classify a \sw subject all the way to the detection threshold (lens
probability 0.95), and then multiplying by the survey inefficiency gives us a
very rough estimate for the effective number of detections corresponding to
the crowd's contribution: these are 2830 and 25 bits for stages 1 and 2
respectively.  These figures are close to the numbers of detections given in
column 7 of the table.  
% The uncertainty in the interpretation of the total
% information generated provides some justification for our focus on the
% expected information gain as a measure of volunteer contribution.
